### 2014-09-06 abstract.tex
abs

In this paper, we present \sysname, a predictive race detector that is able to relax both of these restrictions while guaranteeing soundness, as we prove formally. Thanks to its ability to explore event orderings that violate flow dependencies as well as unexecuted branches, \sysname\ is able to detect x$2.5$ more data races on a representative set of large-scale benchmarks compared to the state of the art in predictive race detection.
\end{abstract}

>>>>

In this paper, we present \sysname, a predictive race detector that is able to relax both of these restrictions while guaranteeing soundness, as we prove formally. Thanks to its ability to explore unexecuted branches as well as event orderings that violate flow dependencies, \sysname\ is able to detect x$2.5$ more data races on a representative set of large-scale benchmarks compared to the state of the art in predictive race detection.
\end{abstract}
